msAggr_seurat

### 2022-01-13 MergeBiomarkWith10X/MergeBiomarkWith10X.Rmd
Minor additions for figures

```{r}
fluor.cols <- names(mfi[, grepl("pos$", names(mfi))])
mfi.norm <- data.frame(matrix(nrow = 0, ncol = length(fluor.cols)))
colnames(mfi.norm) <- fluor.cols
for(sortdate in unique(mfi$sortdate)){
	mfi.subset <- scale(mfi[mfi$sortdate == sortdate, fluor.cols])
	mfi.norm <- rbind(mfi.norm, mfi.subset)
}
mfi.norm["pid"] <- do.call(rbind, strsplit(rownames(mfi.norm), '_'))[,3]
```
Add metadata column
```{r}
tech.integrated <- AddMetaData(tech.integrated, metadata = mfi.norm)
```
now plot some stuff
```{r}
biomark.integrated <- subset(tech.integrated, subset = orig.ident == "biomark")
```
```{r fig.height=12, fig.width=5}
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
```
```{r}
png(filename = paste0(projectName, "_pctVar", integrated.var, "res", integrated.res, "-fluor.png"), height = 2400, width = 800)
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
dev.off()
```
plot umaps
```{r}
for(integrated.col in integrated.ident.list){
		plot.title <- paste0(projectName, "_pctVar", integrated.var, "-mergedEnrichment_OrigIdent-Facet-integratedRes.", gsub("integrated_snn_res.", "", integrated.col))
		myplot <- DimPlot(tech.integrated, 
											group.by = "orig.ident",
											split.by = integrated.col, 
											reduction = "umap", 
											pt.size = 1.5,
											ncol = round(sqrt(length(levels(tech.integrated@meta.data[[sc.col]])))),
											cols = color.palette) + 
			ggtitle(paste0(projectName, "_pctVar", pct.var, "-", integrated.col, " faceted by ", sc.col))
		plot(myplot)

@@

```{r}

>>>>

```{r}
fluor.cols <- names(mfi[, grepl("pos$", names(mfi))])
mfi.norm <- data.frame(matrix(nrow = 0, ncol = length(fluor.cols)))
colnames(mfi.norm) <- fluor.cols
for(sortdate in unique(mfi$sortdate)){
	mfi.subset <- scale(mfi[mfi$sortdate == sortdate, fluor.cols])
	mfi.norm <- rbind(mfi.norm, mfi.subset)
}
mfi.norm["pid"] <- do.call(rbind, strsplit(rownames(mfi.norm), '_'))[,3]
```
Add metadata column
```{r}
tech.integrated <- AddMetaData(tech.integrated, metadata = mfi.norm)
```
now plot some stuff
```{r}
biomark.integrated <- subset(tech.integrated, subset = orig.ident == "CMP")
```
```{r fig.height=12, fig.width=5}
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1)
```
```{r fig.height=12, fig.width=5}
RidgePlot(biomark.integrated, features = c("Cd34pos", "Cd41pos", "Cd9pos", "Cd48pos"), cols = color.palette, ncol = 1, same.y.lims = TRUE)
```
```{r}
png(filename = paste0(projectName, "_pctVar", integrated.var, "res", integrated.res, "-fluor.png"), height = 2400, width = 800)
RidgePlot(biomark.integrated, features = fluor.cols, cols = color.palette, ncol = 1, same.y.lims = TRUE)
dev.off()
```
plot ridgeplot subsets
```{r}
featurelist = c("Cd34pos", "Cd41pos", "Cd9pos", "Cd48pos")
for(fluor in featurelist){
	print(fluor)
	myplot = RidgePlot(biomark.integrated, features = fluor, cols = color.palette, idents = c(4, 5, 7,13), same.y.lims = TRUE, log = TRUE) + xlim(c(-3.5,6))
	png(filename = paste0(projectName, "_pctVar", integrated.var, "res", integrated.res, "_", fluor, "-idents4.5.7.13.png"))
	plot(myplot)
	dev.off()
}
```

plot umaps
```{r}
for(integrated.col in integrated.ident.list){
		plot.title <- paste0(projectName, "_pctVar", integrated.var, "-mergedEnrichment_OrigIdent-Facet-integratedRes.", gsub("integrated_snn_res.", "", integrated.col))
		myplot <- DimPlot(tech.integrated, 
											group.by = "orig.ident",
											split.by = integrated.col, 
											reduction = "umap", 
											pt.size = 1.5,
											ncol = round(sqrt(length(levels(tech.integrated@meta.data[[sc.col]])))),
											cols = color.palette) + 
			ggtitle(paste0(projectName, "_pctVar", pct.var, "-", integrated.col, " faceted by ", sc.col))
		plot(myplot)

@@

```{r}
tech.object <- tech.integrated 
```
```{r}
tech.object@meta.data["collapsed"] <- tech.object@meta.data$integrated_snn_res.1
tech.object@meta.data$collapsed[tech.object@meta.data$collapsed == c(12)] <- 11
tech.object@meta.data$collapsed[tech.object@meta.data$collapsed == c(13)] <- 11
tech.object@meta.data$collapsed[tech.object@meta.data$collapsed == c(14)] <- 11
tech.object@meta.data$collapsed[tech.object@meta.data$collapsed == c(15)] <- 11
tech.object@meta.data$collapsed[tech.object@meta.data$collapsed == c(16)] <- 11
tech.object@meta.data$collapsed[tech.object@meta.data$collapsed == c(17)] <- 11
tech.object@meta.data$collapsed[tech.object@meta.data$collapsed == c(18)] <- 11
tech.object@meta.data$collapsed <- factor(tech.object@meta.data$collapsed)
```
```{r}
features <- c(
	# "Kit", 
	# "Cd34", 
	"Cd48", 
	"Dntt", 
	"Irf8",
	"Lgals3",
	"Ly86",
	# "Mpl",
	"Mpo",
	"Mecom",
	"Pf4",
	# "Itga2b",
	# "Itgb3",
	"Gp1bb", 
	"Vwf",
	"Cd9", 
	"Gata2", 
	"Gata1", 
	"Klf1",
	# "Mt2",
	"Birc5", 
	"Ube2c"
	)
```
```{r}
DoHeatmap(subset(tech.object, downsample = 100), features = features, group.by = "collapsed", group.colors = color.palette)
```

```{r}
colnames(tech.integrated@meta.data)
```

```{r}
seurat.object<- readRDS("../IndividualPops/CMPSubpop_pctVar90.RDS")
seurat.object$collapsed <- tech.object$collapsed
```
```{r}
DimPlot(seurat.object, group.by = "RNA_snn_res.0.5", cols = color.palette)
```
```{r}
# msaggr <- readRDS("../msAggr_seurat/msAggr_seurat_dim26.RDS")
# mscmp <- subset(msaggr, orig.ident == "CMPm2")
# mscmp$collapsed <- tech.integrated$integrated_snn_res.0.5
test.col.pattern <- "collapsed"
target.col.pattern <- "RNA_snn_res."
xlsx_filename <- paste0("msAggr",projectName, "_mergedEnrichmentStats.xlsx")

metadata_overlap_stats(seurat.object = mscmp, 
											 target.col.pattern = target.col.pattern, 
											 test.col.pattern = test.col.pattern, 
											 print_to_screen = TRUE,
											 xlsx_filename = xlsx_filename)
```

```{r}
msaggr <- readRDS("../msAggr_seurat/msAggr_seurat_dim26.RDS")
```
```{r}
source("ScanpyPalette.R")
```

```{r}
msaggr$collapsed <- tech.integrated$integrated_snn_res.0.5
emphasis.palette <- rep("#7F7E7F", 16)
emphasis.palette[5] <- "red"
emphasis.palette[6] <- "blue"
emphasis.palette[8] <- "orange"
emphasis.palette[14] <- "green"
png(filename = "Integrated_clusters.png", height = 800, width = 800)
plot(DimPlot(msaggr, group.by = "collapsed", cols = emphasis.palette, na.value = "#7F7E7F", pt.size = 1))
dev.off()
```

### 2022-01-13 msAggr_seurat/msAggr_seurat.Rmd
Minor additions for figures

```{r}
projectName <- "msAggr_seurat"
jackstraw.dim <- 40
```

@@

## Set favourite resolution
```{r}
object.res <- ".0.5"
Idents(seurat.object) <- paste0("RNA_snn_res", object.res)
length(levels(seurat.object@active.ident))
```

@@

## DGE w/ resolution = 0.5
Strt with comparing all clusters against all other clusters and write out cluster info
calculate `FindAllMarkers()` for different idents and save to new file
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]
# ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
# ident.list <- c("RNA_snn_res.1")
ident.list <- c("RNA_snn_res.0.5")
cut_off <- 1.2
load(file = "/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/mouseIDTable.rda")

for(tested.ident in ident.list){
	ident.res <- gsub("RNA_snn_res", "", tested.ident)
	seurat.object <- SetIdent(seurat.object, value = tested.ident)
	all.markers <- FindAllMarkers(seurat.object)
	# xlsx::write.xlsx(x = all.markers[,c("avg_log2FC", "p_val_adj", "cluster", "gene")], 
	# 								 file = paste0(projectName, "_FindALLMarkers_dim",ndims, ".xlsx"), 
	# 								 sheetName = paste0("res", ident.res), 
	# 								 col.names = TRUE, 
	# 								 row.names = FALSE, 
	# 								 append = TRUE)

@@

	for(cluster in unique(sig.res$cluster)){
		print(paste("writing cluster", cluster))
		new.table <- sig.res[sig.res$cluster == cluster, c("HGNC", "avg_log2FC")]
		new.table <- new.table[order(-new.table$avg_log2FC), ]
		try(dir.create(paste0("RankList_res", ident.res, "_findAll_hgnc/"), showWarnings = FALSE))
		write.table(new.table, file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, ".rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
		write.table(new.table[new.table$avg_log2FC >= cut_off,], file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, "-co", cut_off, "up.rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
		write.table(new.table[new.table$avg_log2FC >= (cut_off)*-1,], file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, "-co", cut_off, "dn.rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
	}
}
```

## topGO with FindAllMarkers
```{r}
source("/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/GoEnrichmentAnalysis.R")
GO_enrichment_function(my_folder = "RankList_res.0.5_findAll_hgnc/", file.pattern = ".rnk", id.type = "symbol")
# GO_enrichment_function(my_folder = "RankList_res.1_findAll_hgnc/", file.pattern = ".rnk", id.type = "symbol")
```

>>>>

```{r}
projectName <- "msAggr_seurat"
jackstraw.dim <- 40

@@

## Set favourite resolution
```{r}
object.res <- ".1"
Idents(seurat.object) <- paste0("RNA_snn_res", object.res)
length(levels(seurat.object@active.ident))
```

@@

## DGE 
Strt with comparing all clusters against all other clusters and write out cluster info
calculate `FindAllMarkers()` for different idents and save to new file
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]
ident.list <- c("RNA_snn_res.1")
# ident.list <- c("RNA_snn_res.0.5")
cut_off <- 1.2
# ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")

load(file = "/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/mouseIDTable.rda")

# for(tested.ident in ident.list){
# 	ident.res <- gsub("RNA_snn_res", "", tested.ident)
# 	seurat.object <- SetIdent(seurat.object, value = tested.ident)
# 	all.markers <- FindAllMarkers(seurat.object)
all.markers <- data.frame(all.markers %>% group_by(cluster))
top100 <- data.frame(all.markers %>% group_by(cluster) %>% top_n(n = 100, wt = absValue))
	xlsx::write.xlsx(x = all.markers[,c("avg_log2FC", "p_val_adj", "cluster", "gene")],
									 file = paste0(projectName, "_FindALLMarkers_dim",ndims, ".xlsx"),
									 sheetName = paste0("res", ident.res),
									 col.names = TRUE,
									 row.names = FALSE,
									 append = TRUE)
		xlsx::write.xlsx(x = data.frame(top100[,c("avg_log2FC", "p_val_adj", "cluster", "gene")]),
									 file = paste0(projectName, "_FindALLMarkers_dim",ndims, "-top100.xlsx"),
									 sheetName = 'top100',
									 col.names = TRUE,
									 row.names = FALSE,
									 append = FALSE)

@@

	for(cluster in unique(sig.res$cluster)){
		print(paste("writing cluster", cluster))
		new.table <- sig.res[sig.res$cluster == cluster, c("HGNC", "avg_log2FC")]
		new.table <- new.table[order(-new.table$avg_log2FC), ]
		try(dir.create(paste0("RankList_res", ident.res, "_findAll_hgnc/"), showWarnings = FALSE))
		write.table(new.table, file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, ".rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
		# write.table(new.table[new.table$avg_log2FC >= cut_off,], file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, "-co", cut_off, "up.rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
		# write.table(new.table[new.table$avg_log2FC >= (cut_off)*-1,], file = paste0("RankList_res", ident.res, "_findAll_hgnc/res", ident.res, "_cluster", cluster, "-co", cut_off, "dn.rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
		}

		#top 100		
	HGNC <- with(mouseIDTable, mouseIDTable$HGNC[match(top100$gene, mouseIDTable$MGI)])
	top100$HGNC <- HGNC
	sig.res <- top100[top100$p_val_adj <= 0.05, ]
	sig.res <- sig.res[c("avg_log2FC", "HGNC", "cluster")]
	sig.res <- sig.res[!(sig.res$HGNC == "" | is.na(sig.res$HGNC)),] # GSEA will fail if there are any blanks or NAs in the table
	sig.res <- sig.res[]

	for(cluster in unique(sig.res$cluster)){
		print(paste("writing cluster", cluster))
		new.table <- sig.res[sig.res$cluster == cluster, c("HGNC", "avg_log2FC")]
		new.table <- new.table[order(-new.table$avg_log2FC), ]
		try(dir.create(paste0("RankList_res", ident.res, "_findAll_hgnc_top100/"), showWarnings = FALSE))
		write.table(new.table, file = paste0("RankList_res", ident.res, "_findAll_hgnc_top100/res", ident.res, "_cluster", cluster, "-top100.rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
		# write.table(new.table[new.table$avg_log2FC >= cut_off,], file = paste0("RankList_res", ident.res, "_findAll_hgnc_top100/res", ident.res, "_cluster", cluster, "-co", cut_off, "top100up.rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
		# write.table(new.table[new.table$avg_log2FC >= (cut_off)*-1,], file = paste0("RankList_res", ident.res, "_findAll_hgnc_top100/res", ident.res, "_cluster", cluster, "-co", cut_off, "top100dn.rnk"), quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t", )
}
```

## topGO with FindAllMarkers
```{r}
source("/Users/heustonef/Desktop/10XGenomicsData/msAggr_scRNASeq/RFunctions/GoEnrichmentAnalysis.R")
# GO_enrichment_function(my_folder = "RankList_res.0.5_findAll_hgnc/", file.pattern = ".rnk", id.type = "symbol")
GO_enrichment_function(my_folder = "RankList_res.1_findAll_hgnc/", file.pattern = ".rnk", id.type = "symbol")
GO_enrichment_function(my_folder = "backups/RankList_res.1_findAll_hgnc/", file.pattern = "up.rnk", id.type = "symbol")
```

write table of cluster IDs
```{r}
write.table(seurat.object@meta.data, file = "msAggr_SeuratMetaData.txt", row.names = row.names(seurat.object@meta.data), sep = "\t", col.names = TRUE, quote = FALSE)
```
